### 2015-05-12 whoop.tex
update

We also optimize the use of function pointers. LLVM and SMACK do not perform context-sensitive translation, which means that a function that accepts a function pointer as an argument, can arbitrarily call any possible method that corresponds to that function pointer regardless of call site. To increase precision, Chauffeur analyses the AST of the original program and attempts to infer context-sensitive function pointer use information. This information is the used by \whoop to increase precision. To be sound, this optimization is conservative: if no information can be extracted for a function pointer at a call site, then \whoop uses the original over-approximated function.

>>>>

%We also optimize the use of function pointers. LLVM and SMACK do not perform context-sensitive translation, which means that a function that accepts a function pointer as an argument, can arbitrarily call any possible method that corresponds to that function pointer regardless of call site. To increase precision, Chauffeur analyses the AST of the original program and attempts to infer context-sensitive function pointer use information. This information is the used by \whoop to increase precision. To be sound, this optimization is conservative: if no information can be extracted for a function pointer at a call site, then \whoop uses the original over-approximated function.
